Title

### 2023-04-02 Paper/PAPER.tex
delete paper

    At the very last, we analyze the strengths and weaknesses of our model as well as its
sensitivity, whose results show that our model has high robustness, precision and accuracy.
After that, a memo is attached.

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
    \vspace{5pt}
    \textbf{Keywords}: TODO.

@@

\textbf{Problem (e) :}
\begin{itemize}
    \item Create a one-to two-page report with well-chosen graphics to assist the Hong Kong sailboat broker to understand your findings.
\end{itemize}
%我们的工作
\subsection{Our work \& Model Overview}
We do such things ...

\begin{enumerate}[\bfseries 1.]
    \item We do ...
    \item We do ...
    \item We do ...
\end{enumerate}
\section{Assumptions and Justififications}
% 问题假设
\subsection{Assumptions}
To simplify our problems, we make the following basic assumptions, each of which is
adequately justified.
\begin{itemize}
    \item The price of used sailboats is solely determined by the factors in the dataset.
    \item The factors in the dataset are independent and unrelated.
    \item The data in the dataset are all real, reasonable, and follow a certain pattern.
    \item The pricing required by a broker should be reasonable and in accordance with market rules, rather than false pricing.
\end{itemize}
%符号含义
\subsection{Notations}
\ 
% 三线表示例
\begin{table}[!htbp]
\begin{center}
\begin{tabular}{cl}
	\toprule
	\multicolumn{1}{m{3cm}}{\centering Symbol}
	&\multicolumn{1}{m{8cm}}{\centering Definition}\\
	\midrule
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	\bottomrule
\end{tabular}
\end{center}
\end{table}
\section{Data Exploration}
\subsection{Data Cleaning}
First of all, we turn the \textbf{\texttt{xlsx}} format data sheet into \textbf{\texttt{csv}} format. 
The conversion causes some minor errors like extra spaces and unexcepted characters which can be easily filtered out by text editor and python string operating functions like \textbf{\texttt{strip()}} or so.

@@

@@

\subsection{Data Augmentation}
We collect and organize more additional features of a given sailboat(such as \textbf{beam}, \textbf{draft}, \textbf{displacement}, \textbf{cabins}, etc.),
and the \textbf{2020 per capita GDP data} of the relevant regions, 
greatly enriching the diversity of the data and expanding the dataset size. 
These efforts lay a solid foundation for subsequent modeling.
\subsection{Data Analysis}

\section{The Prediction Model of Used Sailboat Prices}
\subsection{The Establishment of The Model}
\subsection{Model Validation}
\subsection{Model Accuracy Analysis}

>>>>

    At the very last, we analyze the strengths and weaknesses of our model as well as its
sensitivity, whose results show that our model has high robustness, precision and accuracy.
After that, a report is attached.

    % 美赛论文中无需注明关键字。若您一定要使用，
    % 请将以下两行的注释号 '%' 去除，以使其生效
    \vspace{5pt}
    \textbf{Keywords}: heuristic hierarchical multiple regression, deep forest.

@@

\textbf{Problem (e) :}
\begin{itemize}
    \item Create a one-to two-page report with well-chosen graphics to assist the Hong Kong sailboat broker to understand your findings.
\end{itemize}
%我们的工作
\subsection{Our work \& Model Overview}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth]{Model.png}
    \caption{Model Framework}\label{fig:Model}
\end{figure}

We propose a model framework as shown in Figure \ref{fig:Model}, The model takes \texttt{Year}, \texttt{Region}, \texttt{Variant} as inputs, 
, \texttt{Price} as output, and performs a heuristic hierarchical multiple regression. 
Specifically, in each regression layer, one variable is denormalized, and the other two variables are normalized. 
The obtained \texttt{Price} at this time is used as the Effect of this variable. 
At the same time, the fitting result is used as the baseline for normalization in the next layer and is involved in the regression. 
This process is iterated continuously until the model trains a precise fitting effect.

It is worth noting that we use a heuristic approach for each normalization. 
For larger datasets, we perform regression, while for smaller datasets, we take their average. 
This method greatly improves the accuracy of the model predictions.
\section{Assumptions and Justififications}
% 问题假设
\subsection{Assumptions}
To simplify our problems, we make the following basic assumptions, each of which is
adequately justified.
\begin{itemize}
    \item The price of used sailboats is solely determined by the factors in the dataset.
    \item The factors in the dataset are independent and unrelated.
    \item The data in the dataset are all real, reasonable, and follow a certain pattern.
    \item The pricing required by a broker should be reasonable and in accordance with market rules, rather than false pricing.
\end{itemize}
%符号含义
\subsection{Notations}
\ 
% 三线表示例
\begin{table}[!htbp]
\begin{center}
\begin{tabular}{cl}
	\toprule
	\multicolumn{1}{m{3cm}}{\centering Symbol}
	&\multicolumn{1}{m{8cm}}{\centering Definition}\\
	\midrule
	$A$&the first one\\
	$b$&the second one\\
	$\alpha$ &the last one\\
	\bottomrule
\end{tabular}
\end{center}
\end{table}
\section{Data Exploration}
\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth]{Data.png}
    \caption{Data Exploration}\label{fig:Data}
\end{figure}

\subsection{Data Cleaning}
First of all, we turn the \textbf{\texttt{xlsx}} format data sheet into \textbf{\texttt{csv}} format. 
The conversion causes some minor errors like extra spaces and unexcepted characters which can be easily filtered out by text editor and python string operating functions like \textbf{\texttt{strip()}} or so.

@@

Further more, we merge \textbf{Make} and \textbf{Variant} into a single feature, which we refer to as \textbf{Variant}.

@@

\subsection{Data Analysis}

\subsection{Data Augmentation}
We collect and organize more additional features of a given sailboat(such as \textbf{beam}, \textbf{draft}, \textbf{displacement}, \textbf{cabins}, etc.),
and the \textbf{2020 per capita GDP data} of the relevant regions, 
greatly enriching the diversity of the data and expanding the dataset size. 
These efforts lay a solid foundation for subsequent modeling.

\section{The Prediction Model of Used Sailboat Prices}
\subsection{The Establishment of The Model}

\subsection{Model Validation}
\subsection{Model Accuracy Analysis}
